A Large-Scale Study of the Use of Eval in R

### 2020-08-24 inst/paper/main.tex
wip

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\c{1} and a max of \c{10,000}). Table~\ref{A} details the usage of \eval
across the corpus.  The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and
maximum number of calls for any given run, and A is the mean number of calls
per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.

@@

The following table will be split up:

@@

All the \TotalFileCount files in our corpus call eval. \CoreEvalFileCount
(\CoreEvalFilePerc) call only core evals, \AllEvalFileCount (\AllEvalFilePerc)
call both package and core evals; and, \PackageEvalFileCount
(\PackageEvalFilePerc) call only package evals. Of the \AllEvalFileCount
(\AllEvalFilePerc) files that call both package and base eval,
\EightyCoreEvalFilePerc (\EightyCoreEvalFileCount) files make over 80\% eval
calls to core evals.

Of the \missingNumber packages in our corpus, only \missingNumber packages call
eval. \ref{table:top-ten-package-summary} shows the number of calls to eval made
by the ten most frequent callers to eval. These packages together have
\missingNumber callsites and account for \missingPercentage calls to eval.
Furthermore, the top ten callsites account for \missingPercentage of package
eval calls. A single callsite of \TopTenPackageNameA accounts for over
\missingPercentage calls to eval.

>>>>

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\c{1} and a max of \c{10,000}). Table~\ref{A} details the usage of \eval
across the corpus.  The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and
maximum number of calls for any given run, and A is the mean number of calls
per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.  {\bf <The following
  will be changed. The file level stuff is less useful than package level.>}
All the \TotalFileCount files in our corpus call eval. \CoreEvalFileCount
(\CoreEvalFilePerc) call only core evals, \AllEvalFileCount
(\AllEvalFilePerc) call both package and core evals; and,
\PackageEvalFileCount (\PackageEvalFilePerc) call only package evals. Of the
\AllEvalFileCount (\AllEvalFilePerc) files that call both package and base
eval, \EightyCoreEvalFilePerc (\EightyCoreEvalFileCount) files make over
80\% eval calls to core evals. Of the \missingNumber packages in our corpus,
only \missingNumber packages call eval. \ref{table:top-ten-package-summary}
shows the number of calls to eval made by the ten most frequent callers to
eval. These packages together have \missingNumber callsites and account for
\missingPercentage calls to eval.  Furthermore, the top ten callsites
account for \missingPercentage of package eval calls. A single callsite of
\TopTenPackageNameA accounts for over \missingPercentage calls to eval.

@@

The following table will be replaced. {\bf <At this point separating between
  the different kinds of evals is distracting. We have not argued why it is
  important.>}

@@
